Manuscript 2: Child Health Outcomes

### 2021-10-05 papertwo_child_health.Rmd
Update to include analysis for health behavior paper, and to revise child health analysis using Bayesian models.

---
title: "Manuscript 2: Child Health Outcomes"
author: "Elizabeth Chase"
date: "5/10/2021"
output: pdf_document
---

@@

library(tidyverse)
library(gridExtra)
library(RColorBrewer)
library(tableone)
library(latex2exp)
library(labelled)
library(kableExtra)
library(logistf)
library(ARTool)
library(lme4)

@@

subadult <- mutate(adult_clean_eliz, parbloodtestf = blood_test_after_april_2014, parbllf = elevated_lead_after_april_2014, parrashesf = rashes_after_april_2014, parhairf = hairloss_after_april_2014, parnausf = nausea_after_april_2014, parirrf = irritable_after_april_2014, parbloodtestc = getscreened, parbllc = elevated_collapse, parrashesc = rash_collapse, parhairc = hair_collapse, parnausc = nausea_collapse, parirrc = irritable_collapse, paroverall = overall_collapse) %>% select(inclusion, unique_id, age, gender, collapserace, collapseeduc, have_health_insurance, public_benefits, water_exaggerated, children_health_harmed, trust_government_in_future, drink_tap_in_three_years, satisfied_flint_government, satisfied_state_government, satisfied_federal_government, political_affiliation, nightmares, avoided_thinking_crisis, onguard_watchful, numb_detached, felt_guilty, ptsdscore, phq, parbloodtestf, parbllf, parrashesf, parhairf, parnausf, parirrf, parbloodtestc, parbllc, parrashesc, parhairc, parnausc, parirrc, paroverall, confidants2, number_children, employ_status, num_time_notice, watertestbinary, current_zip, waterlinereplaced)

@@

#child_adult$gettested <- ifelse(child_adult$blood_test_after_april_2014=="Yes" & child_adult$blood_test_before_april_2014=="No", 1, ifelse(is.na(child_adult$blood_test_after_april_2014) | is.na(child_adult$blood_test_before_april_2014), NA_real_, 0))

@@

#child_adult$elevbll <- ifelse(child_adult$elevated_lead_after_april_2014=="Yes" & child_adult$elevated_lead_before_april_2014=="No", 1, ifelse(is.na(child_adult$elevated_lead_after_april_2014) | is.na(child_adult$elevated_lead_before_april_2014), NA_real_, 0))

@@

#child_adult$rash <- ifelse(child_adult$rash_after_april_2014=="Yes" & child_adult$rash_before_april_2014=="No", 1, ifelse(is.na(child_adult$rash_after_april_2014) | is.na(child_adult$rash_before_april_2014), NA_real_, 0))

@@

#child_adult$hair <- ifelse(child_adult$hairloss_after_april_2014=="Yes" & child_adult$hairloss_before_april_2014=="No", 1, ifelse(is.na(child_adult$hairloss_after_april_2014) | is.na(child_adult$hairloss_before_april_2014), NA_real_, 0))

@@

#child_adult$learn <- ifelse(child_adult$learning_after_april_2014=="Yes" & child_adult$learning_before_april_2014=="No", 1, ifelse(is.na(child_adult$learning_after_april_2014) | is.na(child_adult$learning_before_april_2014), NA_real_, 0))

@@

#child_adult$hyper <- ifelse(child_adult$hyper_after_april_2014=="Yes" & child_adult$hyper_before_april_2014=="No", 1, ifelse(is.na(child_adult$hyper_after_april_2014) | is.na(child_adult$hyper_before_april_2014), NA_real_, 0))

@@

#child_adult$irritable <- ifelse(child_adult$irritable_after_april_2014=="Yes" & child_adult$irritable_before_april_2014=="No", 1, ifelse(is.na(child_adult$irritable_after_april_2014) | is.na(child_adult$irritable_before_april_2014), NA_real_, 0))

@@

symp_sub <- select(child_adult, gettested, elevbll, rash, hair, learn, hyper, irritable)

@@

exam <- select(child_adult, child, unique_id, relationship, age.x, gender.x, public_benefits, gettested, elevbll, rash, hair, learn, hyper, irritable, overall_symp, racecollapse, blood_test_after_april_2014, water_exaggerated)

@@

@@

@@

## Multivariable modeling results

@@

##watersource_model <- glmer(bottledwater ~ gender.x + age.x + racecollapse + pubben + (1 | unique_id), data = child_adult, family = "binomial") ##issues with convergence; did not include

##summary(watersource_model)

#For getting tested:
tested_model_noadult <- glmer(gettested ~ gender.x + age.x + racecollapse + pubben + (1 | unique_id), data = child_adult, family = "binomial")
tested_model_adult <- glmer(gettested ~ gender.x + age.x + racecollapse + pubben + water_exaggeratedbinary + (1 | unique_id), data = child_adult, family = "binomial")

summary(tested_model_noadult)
summary(tested_model_adult)

effects_mat <- data.frame("Outcome" = rep("Get tested", 6), "Variable" = c("Male gender (ref: Female gender)", "Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Receives public benefits (ref: No benefits)", "Water crisis was exaggerated (ref: Crisis not exaggerated)"), "Estimate" = c(summary(tested_model_noadult)$coefficients[-1,1], summary(tested_model_adult)$coefficients[7,1]), "StErr" = c(summary(tested_model_noadult)$coefficients[-1,2], summary(tested_model_adult)$coefficients[7,2]), "Pvalue" = c(summary(tested_model_noadult)$coefficients[-1,4], summary(tested_model_adult)$coefficients[7,4]))

#For having elevated BLLs:
#bll_model_noadult <- glmer(elevbll ~ gender.x + age.x + racecollapse + pubben + (1 | unique_id), data = child_adult, family = "binomial")
#bll_model_adult <- glmer(elevbll ~ gender.x + scale(age.x) + racecollapse + pubben + as.numeric(blood_test_after_april_2014=="Yes") + (1 | unique_id), data = child_adult, family = "binomial") # Not included due to convergence issues

#summary(bll_model_noadult)
#summary(bll_model_adult)

#subdat <- data.frame("Outcome" = rep("Elevated BLLs", 5), "Variable" = c("Gender", "Age", "Race-Other", "Race-White", "Public Benefits"), "Estimate" = c(summary(bll_model_noadult)$coefficients[-1,1]), "StErr" = c(summary(bll_model_noadult)$coefficients[-1,2]), "Pvalue" = c(summary(bll_model_noadult)$coefficients[-1,4]))

#effects_mat <- rbind(effects_mat, subdat)

#For having rashes:
rash_model_noadult <- glmer(rash ~ gender.x + age.x + racecollapse + pubben + (1 | unique_id), data = child_adult, family = "binomial")
summary(rash_model_noadult)
rash_model_adult <- glmer(rash ~ gender.x + age.x + racecollapse + pubben + as.numeric(blood_test_after_april_2014=="Yes") + (1 | unique_id), data = child_adult, family = "binomial")
summary(rash_model_adult)

subdat <- data.frame("Outcome" = rep("Rashes", 6), "Variable" = c("Male gender (ref: Female gender)", "Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Receives public benefits (ref: No benefits)", "Child screened for BLLs (ref: Child not screened for BLLs"), "Estimate" = c(summary(rash_model_noadult)$coefficients[-1,1], summary(rash_model_adult)$coefficients[7,1]), "StErr" = c(summary(rash_model_noadult)$coefficients[-1,2], summary(rash_model_adult)$coefficients[7,2]), "Pvalue" = c(summary(rash_model_noadult)$coefficients[-1,4], summary(rash_model_adult)$coefficients[7,4]))

@@

#For having hair loss:
#hair_model_noadult <- glmer(hair ~ gender.x + scale(age.x) + racecollapse + pubben + (1 | unique_id), data = child_adult, family = "binomial") ## convergence issues; did not include
#summary(hair_model_noadult)
#hair_model_adult <- glmer(hair ~ gender.x + scale(age.x) + racecollapse + pubben + as.numeric(blood_test_after_april_2014=="Yes") + (1 | unique_id), data = child_adult, family = "binomial") ## convergence issues; did not include
#summary(hair_model_adult)

#subdat <- data.frame("Outcome" = rep("Hairloss", 6), "Variable" = c("Male gender (ref: Female gender)", "Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Receives public benefits (ref: No benefits)", "Child screened for BLLs (ref: Child not screened for BLLs"), "Estimate" = c(summary(hair_model_noadult)$coefficients[-1,1], summary(hair_model_adult)$coefficients[7,1]), "StErr" = c(summary(hair_model_noadult)$coefficients[-1,2], summary(hair_model_adult)$coefficients[7,2]), "Pvalue" = c(summary(hair_model_noadult)$coefficients[-1,4], summary(hair_model_adult)$coefficients[7,4]))

#effects_mat <- rbind(effects_mat, subdat)

#For having learning delays:
learn_model_noadult <- glmer(learn ~ gender.x + age.x + racecollapse + pubben + (1 | unique_id), data = child_adult, family = "binomial")
summary(learn_model_noadult)

learn_model_layer2 <- glmer(learn ~ gender.x + age.x + racecollapse + pubben + as.numeric(blood_test_after_april_2014=="Yes") + (1 | unique_id), data = child_adult, family = "binomial")
summary(learn_model_layer2)

subdat <- data.frame("Outcome" = rep("Learning Delays", 6), "Variable" = c("Male gender (ref: Female gender)", "Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Receives public benefits (ref: No benefits)", "Child screened for BLLs (ref: Child not screened for BLLs"), "Estimate" = c(summary(learn_model_noadult)$coefficients[-1,1], summary(learn_model_layer2)$coefficients[7,1]), "StErr" = c(summary(learn_model_noadult)$coefficients[-1,2], summary(learn_model_layer2)$coefficients[7,2]), "Pvalue" = c(summary(learn_model_noadult)$coefficients[-1,4], summary(learn_model_layer2)$coefficients[7,4]))

@@

#For having hyperactivity:
hyper_model_noadult <- glmer(hyper ~ gender.x + scale(age.x) + racecollapse + pubben + (1 | unique_id), data = child_adult, family = "binomial")
summary(hyper_model_noadult)

hyper_model_layer2 <- glmer(hyper ~ gender.x + age.x + racecollapse + pubben + as.numeric(blood_test_after_april_2014=="Yes") + (1 | unique_id), data = child_adult, family = "binomial")
summary(hyper_model_layer2)

subdat <- data.frame("Outcome" = rep("Hyperactivity", 6), "Variable" = c("Male gender (ref: Female gender)", "Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Receives public benefits (ref: No benefits)", "Child screened for BLLs (ref: Child not screened for BLLs"), "Estimate" = c(summary(hyper_model_noadult)$coefficients[-1,1], summary(hyper_model_layer2)$coefficients[7,1]), "StErr" = c(summary(hyper_model_noadult)$coefficients[-1,2], summary(hyper_model_layer2)$coefficients[7,2]), "Pvalue" = c(summary(hyper_model_noadult)$coefficients[-1,4], summary(hyper_model_layer2)$coefficients[7,4]))

@@

#For having irritability:
irr_model_noadult <- glmer(irritable ~ gender.x + age.x + racecollapse + pubben + (1 | unique_id), data = child_adult, family = "binomial")
summary(irr_model_noadult)
irr_model_adult <- glmer(irritable ~ gender.x + age.x + racecollapse + pubben + as.numeric(blood_test_after_april_2014=="Yes") + (1 | unique_id), data = child_adult, family = "binomial")
summary(irr_model_adult)

subdat <- data.frame("Outcome" = rep("Irritability", 6), "Variable" = c("Male gender (ref: Female gender)", "Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Receives public benefits (ref: No benefits)", "Child screened for BLLs (ref: Child not screened for BLLs"), "Estimate" = c(summary(irr_model_noadult)$coefficients[-1,1], summary(irr_model_adult)$coefficients[7,1]), "StErr" = c(summary(irr_model_noadult)$coefficients[-1,2], summary(irr_model_adult)$coefficients[7,2]), "Pvalue" = c(summary(irr_model_noadult)$coefficients[-1,4], summary(irr_model_adult)$coefficients[7,4]))

@@

#For overall symptoms:
overall_model_noadult <- lmer(overall_symp ~ gender.x + age.x + racecollapse + pubben + (1 | unique_id), data = child_adult)
summary(overall_model_noadult)

overall_model_adult <- lmer(overall_symp ~ gender.x + age.x + racecollapse + pubben + as.numeric(blood_test_after_april_2014=="Yes") + water_exaggeratedbinary + (1 | unique_id), data = child_adult)
summary(overall_model_adult)

subdat <- data.frame("Outcome" = rep("Overall Symptoms", 7), "Variable" = c("Male gender (ref: Female gender)", "Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Receives public benefits (ref: No benefits)", "Child screened for BLLs (ref: Child not screened for BLLs)", "Water crisis was exaggerated (ref: Crisis not exaggerated)"), "Estimate" = c(summary(overall_model_noadult)$coefficients[-1,1], summary(overall_model_adult)$coefficients[7:8,1]), "StErr" = c(summary(overall_model_noadult)$coefficients[-1,2], summary(overall_model_adult)$coefficients[7:8,2]), "Pvalue" = pnorm(c(summary(overall_model_noadult)$coefficients[-1,3], summary(overall_model_adult)$coefficients[7:8,3]), lower.tail = FALSE))

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE}
effects_mat$BHpvalue <- p.adjust(effects_mat$Pvalue, method="BH")

effects_mat$lower <- case_when(
  effects_mat$Outcome=="Overall Symptoms" ~ effects_mat$Estimate - 1.96*effects_mat$StErr,
  effects_mat$Outcome!="Overall Symptoms" ~ exp(effects_mat$Estimate - 1.96*effects_mat$StErr)
)

effects_mat$upper <- case_when(
  effects_mat$Outcome=="Overall Symptoms" ~ effects_mat$Estimate + 1.96*effects_mat$StErr,
  effects_mat$Outcome!="Overall Symptoms" ~ exp(effects_mat$Estimate + 1.96*effects_mat$StErr)
)

effects_mat$effect <- case_when(
  effects_mat$Outcome=="Overall Symptoms" ~ effects_mat$Estimate,
  effects_mat$Outcome!="Overall Symptoms" ~ exp(effects_mat$Estimate)
)

effects_mat$label <- paste0(round(effects_mat$effect, digits=1), " (", round(effects_mat$lower, digits = 1), ", ", round(effects_mat$upper, digits = 1), ")")

pretty_effects <- select(effects_mat, Outcome, Variable, label, BHpvalue)
pretty_effects$BHpvalue <- round(pretty_effects$BHpvalue, 3)
rownames(pretty_effects) <- NULL

kable(pretty_effects, col.names = c("Outcome", "Predictor", "Odds Ratio (95% CI)", "P-value"))
```

Note that these modeling results doesn't include one important outcomes: child water source. I was unable to get this model to fit stably because of the small number of children not drinking bottled water. In addition, I couldn't consider the effect of the caregiver believing the water crisis was exaggerated on most of the outcomes because of convergence issues, and similarly with the relationship between the child being tested and the child having elevated BLLs.

>>>>

---
title: "Manuscript 2: Child Health Outcomes"
author: "Elizabeth Chase"
date: "10/5/2021"
output: pdf_document
---

@@

library(tidyverse)
library(gridExtra)
library(RColorBrewer)
library(tableone)
library(latex2exp)
library(labelled)
library(kableExtra)
library(logistf)
library(ARTool)
library(lme4)
library(rstanarm)

@@

subadult <- mutate(adult_clean_eliz, parbloodtestf = blood_test_after_april_2014, parbllf = elevated_lead_after_april_2014, parrashesf = rashes_after_april_2014, parhairf = hairloss_after_april_2014, parnausf = nausea_after_april_2014, parirrf = irritable_after_april_2014, parbloodtestc = getscreened, parbllc = elevated_collapse, parrashesc = rash_collapse, parhairc = hair_collapse, parnausc = nausea_collapse, parirrc = irritable_collapse, paroverall = overall_collapse) %>% dplyr::select(inclusion, unique_id, age, gender, collapserace, collapseeduc, have_health_insurance, public_benefits, water_exaggerated, children_health_harmed, trust_government_in_future, drink_tap_in_three_years, satisfied_flint_government, satisfied_state_government, satisfied_federal_government, political_affiliation, nightmares, avoided_thinking_crisis, onguard_watchful, numb_detached, felt_guilty, ptsdscore, phq, parbloodtestf, parbllf, parrashesf, parhairf, parnausf, parirrf, parbloodtestc, parbllc, parrashesc, parhairc, parnausc, parirrc, paroverall, confidants2, number_children, employ_status, num_time_notice, watertestbinary, current_zip, waterlinereplaced)

@@

@@

@@

@@

@@

@@

@@

@@

symp_sub <- dplyr::select(child_adult, gettested, elevbll, rash, hair, learn, hyper, irritable)

@@

exam <- dplyr::select(child_adult, child, unique_id, relationship, age.x, gender.x, public_benefits, gettested, elevbll, rash, hair, learn, hyper, irritable, overall_symp, racecollapse, blood_test_after_april_2014, water_exaggerated)

@@

Note: May 2021

@@

Note: Oct. 2021

This analysis was redone using Bayesian models, in order to meet a reviewer request for models that would not converge using REML. This allows us to address the issues with small sample size and separation in the data.

@@

## Multivariable modeling results (normal priors)

@@

watersource_model <- stan_glmer(bottledwater ~ gender.x + age.x + racecollapse + pubben + water_exaggeratedbinary + gettested + elevbll + (1 | unique_id),
                               data = child_adult, 
                               family = "binomial", seed = 12)

mysum <- summary(watersource_model, pars = c("(Intercept)", "gender.xMale", "age.x", "racecollapseOther", "racecollapseWhite", "pubben", "water_exaggeratedbinary", "gettestedYes", "elevbllYes", "Sigma[unique_id:(Intercept),(Intercept)]"), probs = c(0.025, 0.5, 0.975), digits = 2)

mysum

effects_mat <- data.frame("Outcome" = rep("Child drinks bottled water", 8), "Variable" = c("Male gender (ref: Female gender)", "Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Receives public benefits (ref: No benefits)", "Water crisis was exaggerated (ref: Crisis not exaggerated)", "Child screened for BLLs (ref: Child not screened)", "Child diagnosed with elevated BLLs (ref: Child had normal BLLs)"), "Estimate" = mysum[2:9, 5], "Lower" = mysum[2:9, 4], "Upper" = mysum[2:9, 6])

#For getting tested:
tested_model <- stan_glmer(gettested ~ gender.x + age.x + racecollapse + pubben + water_exaggeratedbinary + (1 | unique_id), data = child_adult, family = "binomial", seed = 13)

mysum <- summary(tested_model, pars = c("(Intercept)", "gender.xMale", "age.x", "racecollapseOther", "racecollapseWhite", "pubben", "water_exaggeratedbinary", "Sigma[unique_id:(Intercept),(Intercept)]"), probs = c(0.025, 0.5, 0.975), digits = 2)

mysum

subdat <- data.frame("Outcome" = rep("Get tested", 6), "Variable" = c("Male gender (ref: Female gender)", "Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Receives public benefits (ref: No benefits)", "Water crisis was exaggerated (ref: Crisis not exaggerated)"), "Estimate" = mysum[2:7, 5], "Lower" = mysum[2:7, 4], "Upper" = mysum[2:7, 6])

@@

#For having elevated BLLs (restricting to children who were screened):
bll_model <- stan_glmer(elevbll ~ gender.x + age.x + racecollapse + pubben + water_exaggeratedbinary + (1 | unique_id), data = filter(child_adult, gettested=="Yes"), family = "binomial", seed = 14)

mysum <- summary(bll_model, pars = c("(Intercept)", "gender.xMale", "age.x", "racecollapseOther", "racecollapseWhite", "pubben", "water_exaggeratedbinary", "Sigma[unique_id:(Intercept),(Intercept)]"), probs = c(0.025, 0.5, 0.975), digits = 2)

mysum

subdat <- data.frame("Outcome" = rep("Elevated BLLs", 6), "Variable" = c("Male gender (ref: Female gender)", "Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Receives public benefits (ref: No benefits)", "Water crisis was exaggerated (ref: Crisis not exaggerated)"), "Estimate" = mysum[2:7, 5], "Lower" = mysum[2:7, 4], "Upper" = mysum[2:7, 6])

@@

#For having rashes:
rash_model <- stan_glmer(rash ~ gender.x + age.x + racecollapse + pubben + water_exaggeratedbinary + gettested  + elevbll + (1 | unique_id), data = child_adult, family = "binomial", seed = 15)

mysum <- summary(rash_model, pars = c("(Intercept)", "gender.xMale", "age.x", "racecollapseOther", "racecollapseWhite", "pubben", "water_exaggeratedbinary", "gettestedYes", "elevbllYes", "Sigma[unique_id:(Intercept),(Intercept)]"), probs = c(0.025, 0.5, 0.975), digits = 2)

mysum

subdat <- data.frame("Outcome" = rep("Rashes", 8), "Variable" = c("Male gender (ref: Female gender)", "Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Receives public benefits (ref: No benefits)", "Water crisis was exaggerated (ref: Crisis not exaggerated)", "Child screened for BLLs (ref: Child not screened)", "Child diagnosed with elevated BLLs (ref: Child had normal BLLs)"), "Estimate" = mysum[2:9, 5], "Lower" = mysum[2:9, 4], "Upper" = mysum[2:9, 6])

@@

#For having hair loss
hair_model <- stan_glmer(hair ~ gender.x + age.x + racecollapse + pubben + water_exaggeratedbinary + gettested + elevbll + (1 | unique_id), data = child_adult, family = "binomial", seed = 16)

mysum <- summary(hair_model, pars = c("(Intercept)", "gender.xMale", "age.x", "racecollapseOther", "racecollapseWhite", "pubben", "water_exaggeratedbinary", "gettestedYes", "elevbllYes", "Sigma[unique_id:(Intercept),(Intercept)]"), probs = c(0.025, 0.5, 0.975), digits = 2)

mysum

subdat <- data.frame("Outcome" = rep("Hair loss", 8), "Variable" = c("Male gender (ref: Female gender)", "Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Receives public benefits (ref: No benefits)", "Water crisis was exaggerated (ref: Crisis not exaggerated)", "Child screened for BLLs (ref: Child not screened)", "Child diagnosed with elevated BLLs (ref: Child had normal BLLs)"), "Estimate" = mysum[2:9, 5], "Lower" = mysum[2:9, 4], "Upper" = mysum[2:9, 6])

@@

#For having learning delays:
learn_model <- stan_glmer(learn ~ gender.x + age.x + racecollapse + pubben + water_exaggeratedbinary + gettested + elevbll + (1 | unique_id), data = child_adult, family = "binomial", seed = 17)

mysum <- summary(learn_model, pars = c("(Intercept)", "gender.xMale", "age.x", "racecollapseOther", "racecollapseWhite", "pubben", "water_exaggeratedbinary", "gettestedYes", "elevbllYes", "Sigma[unique_id:(Intercept),(Intercept)]"), probs = c(0.025, 0.5, 0.975), digits = 2)

mysum

subdat <- data.frame("Outcome" = rep("Learning delays", 8), "Variable" = c("Male gender (ref: Female gender)", "Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Receives public benefits (ref: No benefits)", "Water crisis was exaggerated (ref: Crisis not exaggerated)", "Child screened for BLLs (ref: Child not screened)", "Child diagnosed with elevated BLLs (ref: Child had normal BLLs)"), "Estimate" = mysum[2:9, 5], "Lower" = mysum[2:9, 4], "Upper" = mysum[2:9, 6])

#For having hyperactivity:
hyper_model <- stan_glmer(hyper ~ gender.x + age.x + racecollapse + pubben + water_exaggeratedbinary + gettested + elevbll + (1 | unique_id), data = child_adult, family = "binomial", seed = 18)

mysum <- summary(hyper_model, pars = c("(Intercept)", "gender.xMale", "age.x", "racecollapseOther", "racecollapseWhite", "pubben", "water_exaggeratedbinary", "gettestedYes", "elevbllYes", "Sigma[unique_id:(Intercept),(Intercept)]"), probs = c(0.025, 0.5, 0.975), digits = 2)

mysum

subdat <- data.frame("Outcome" = rep("Hyperactivity", 8), "Variable" = c("Male gender (ref: Female gender)", "Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Receives public benefits (ref: No benefits)", "Water crisis was exaggerated (ref: Crisis not exaggerated)", "Child screened for BLLs (ref: Child not screened)", "Child diagnosed with elevated BLLs (ref: Child had normal BLLs)"), "Estimate" = mysum[2:9, 5], "Lower" = mysum[2:9, 4], "Upper" = mysum[2:9, 6])

#For having irritability:
irr_model <- stan_glmer(irritable ~ gender.x + age.x + racecollapse + pubben + water_exaggeratedbinary + gettested + elevbll + (1 | unique_id), data = child_adult, family = "binomial", seed = 19)

mysum <- summary(irr_model, pars = c("(Intercept)", "gender.xMale", "age.x", "racecollapseOther", "racecollapseWhite", "pubben", "water_exaggeratedbinary", "gettestedYes", "elevbllYes", "Sigma[unique_id:(Intercept),(Intercept)]"), probs = c(0.025, 0.5, 0.975), digits = 2)

mysum

subdat <- data.frame("Outcome" = rep("Irritability", 8), "Variable" = c("Male gender (ref: Female gender)", "Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Receives public benefits (ref: No benefits)", "Water crisis was exaggerated (ref: Crisis not exaggerated)", "Child screened for BLLs (ref: Child not screened)", "Child diagnosed with elevated BLLs (ref: Child had normal BLLs)"), "Estimate" = mysum[2:9, 5], "Lower" = mysum[2:9, 4], "Upper" = mysum[2:9, 6])

#For overall symptoms:
overall_model <- stan_lmer(overall_symp ~ gender.x + age.x + racecollapse + pubben + water_exaggeratedbinary + gettested + elevbll + (1 | unique_id), data = child_adult, seed = 20)

mysum <- summary(overall_model, pars = c("(Intercept)", "gender.xMale", "age.x", "racecollapseOther", "racecollapseWhite", "pubben", "water_exaggeratedbinary", "gettestedYes", "elevbllYes", "Sigma[unique_id:(Intercept),(Intercept)]"), probs = c(0.025, 0.5, 0.975), digits = 2)

mysum

subdat <- data.frame("Outcome" = rep("Total Symptoms", 8), "Variable" = c("Male gender (ref: Female gender)", "Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Receives public benefits (ref: No benefits)", "Water crisis was exaggerated (ref: Crisis not exaggerated)", "Child screened for BLLs (ref: Child not screened)", "Child diagnosed with elevated BLLs (ref: Child had normal BLLs)"), "Estimate" = mysum[2:9, 5], "Lower" = mysum[2:9, 4], "Upper" = mysum[2:9, 6])

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE}

effects_mat$lower <- case_when(
  effects_mat$Outcome=="Overall Symptoms" ~ effects_mat$Lower,
  effects_mat$Outcome!="Overall Symptoms" ~ exp(effects_mat$Lower)
)

effects_mat$upper <- case_when(
  effects_mat$Outcome=="Overall Symptoms" ~ effects_mat$Upper,
  effects_mat$Outcome!="Overall Symptoms" ~ exp(effects_mat$Upper)
)

effects_mat$estimate <- case_when(
  effects_mat$Outcome=="Overall Symptoms" ~ effects_mat$Estimate,
  effects_mat$Outcome!="Overall Symptoms" ~ exp(effects_mat$Estimate)
)

effects_mat$label <- paste0(round(effects_mat$estimate, digits=1), " (", round(effects_mat$lower, digits = 1), ", ", round(effects_mat$upper, digits = 1), ")")

pretty_effects <- dplyr::select(effects_mat, Outcome, Variable, label)
rownames(pretty_effects) <- NULL

kable(pretty_effects, col.names = c("Outcome", "Predictor", "Odds Ratio (95% CI)"))
```

## Multivariable modeling results (Cauchy priors for additional regularization)

watersource_model2 <- stan_glmer(bottledwater ~ gender.x + age.x + racecollapse + pubben + water_exaggeratedbinary + gettested + elevbll + (1 | unique_id),
                               data = child_adult, 
                               family = "binomial", seed = 21,
                               prior = cauchy(location = 0,
                                              scale = 2.5,
                                              autoscale = TRUE))

mysum <- summary(watersource_model2, pars = c("(Intercept)", "gender.xMale", "age.x", "racecollapseOther", "racecollapseWhite", "pubben", "water_exaggeratedbinary", "gettestedYes", "elevbllYes", "Sigma[unique_id:(Intercept),(Intercept)]"), probs = c(0.025, 0.5, 0.975), digits = 2)

mysum

effects_mat2 <- data.frame("Outcome" = rep("Child drinks bottled water", 8), "Variable" = c("Male gender (ref: Female gender)", "Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Receives public benefits (ref: No benefits)", "Water crisis was exaggerated (ref: Crisis not exaggerated)", "Child screened for BLLs (ref: Child not screened)", "Child diagnosed with elevated BLLs (ref: Child had normal BLLs)"), "Estimate" = mysum[2:9, 5], "Lower" = mysum[2:9, 4], "Upper" = mysum[2:9, 6])

#For getting tested:
tested_model2 <- stan_glmer(gettested ~ gender.x + age.x + racecollapse + pubben + water_exaggeratedbinary + (1 | unique_id), data = child_adult, family = "binomial", seed = 22,
                               prior = cauchy(location = 0,
                                              scale = 2.5,
                                              autoscale = TRUE))

mysum <- summary(tested_model2, pars = c("(Intercept)", "gender.xMale", "age.x", "racecollapseOther", "racecollapseWhite", "pubben", "water_exaggeratedbinary", "Sigma[unique_id:(Intercept),(Intercept)]"), probs = c(0.025, 0.5, 0.975), digits = 2)

mysum

subdat <- data.frame("Outcome" = rep("Get tested", 6), "Variable" = c("Male gender (ref: Female gender)", "Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Receives public benefits (ref: No benefits)", "Water crisis was exaggerated (ref: Crisis not exaggerated)"), "Estimate" = mysum[2:7, 5], "Lower" = mysum[2:7, 4], "Upper" = mysum[2:7, 6])

effects_mat2 <- rbind(effects_mat2, subdat)

#For having elevated BLLs (restricting to children who got screened):
bll_model2 <- stan_glmer(elevbll ~ gender.x + age.x + racecollapse + pubben + water_exaggeratedbinary + (1 | unique_id), data = filter(child_adult, gettested=="Yes"), family = "binomial", seed = 23,
                               prior = cauchy(location = 0,
                                              scale = 2.5,
                                              autoscale = TRUE))

mysum <- summary(bll_model2, pars = c("(Intercept)", "gender.xMale", "age.x", "racecollapseOther", "racecollapseWhite", "pubben", "water_exaggeratedbinary", "Sigma[unique_id:(Intercept),(Intercept)]"), probs = c(0.025, 0.5, 0.975), digits = 2)

mysum

subdat <- data.frame("Outcome" = rep("Elevated BLLs", 6), "Variable" = c("Male gender (ref: Female gender)", "Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Receives public benefits (ref: No benefits)", "Water crisis was exaggerated (ref: Crisis not exaggerated)"), "Estimate" = mysum[2:7, 5], "Lower" = mysum[2:7, 4], "Upper" = mysum[2:7, 6])

effects_mat2 <- rbind(effects_mat2, subdat)

#For having rashes:
rash_model2 <- stan_glmer(rash ~ gender.x + age.x + racecollapse + pubben + water_exaggeratedbinary + gettested  + elevbll + (1 | unique_id), data = child_adult, family = "binomial", seed = 24,
                               prior = cauchy(location = 0,
                                              scale = 2.5,
                                              autoscale = TRUE))

mysum <- summary(rash_model2, pars = c("(Intercept)", "gender.xMale", "age.x", "racecollapseOther", "racecollapseWhite", "pubben", "water_exaggeratedbinary", "gettestedYes", "elevbllYes", "Sigma[unique_id:(Intercept),(Intercept)]"), probs = c(0.025, 0.5, 0.975), digits = 2)

mysum

subdat <- data.frame("Outcome" = rep("Rashes", 8), "Variable" = c("Male gender (ref: Female gender)", "Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Receives public benefits (ref: No benefits)", "Water crisis was exaggerated (ref: Crisis not exaggerated)", "Child screened for BLLs (ref: Child not screened)", "Child diagnosed with elevated BLLs (ref: Child had normal BLLs)"), "Estimate" = mysum[2:9, 5], "Lower" = mysum[2:9, 4], "Upper" = mysum[2:9, 6])

effects_mat2 <- rbind(effects_mat2, subdat)

#For having hair loss
hair_model2 <- stan_glmer(hair ~ gender.x + age.x + racecollapse + pubben + water_exaggeratedbinary + gettested + elevbll + (1 | unique_id), data = child_adult, family = "binomial", seed = 25,
                               prior = cauchy(location = 0,
                                              scale = 2.5,
                                              autoscale = TRUE))

mysum <- summary(hair_model2, pars = c("(Intercept)", "gender.xMale", "age.x", "racecollapseOther", "racecollapseWhite", "pubben", "water_exaggeratedbinary", "gettestedYes", "elevbllYes", "Sigma[unique_id:(Intercept),(Intercept)]"), probs = c(0.025, 0.5, 0.975), digits = 2)

mysum

subdat <- data.frame("Outcome" = rep("Hair loss", 8), "Variable" = c("Male gender (ref: Female gender)", "Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Receives public benefits (ref: No benefits)", "Water crisis was exaggerated (ref: Crisis not exaggerated)", "Child screened for BLLs (ref: Child not screened)", "Child diagnosed with elevated BLLs (ref: Child had normal BLLs)"), "Estimate" = mysum[2:9, 5], "Lower" = mysum[2:9, 4], "Upper" = mysum[2:9, 6])

effects_mat2 <- rbind(effects_mat2, subdat)

#For having learning delays:
learn_model2 <- stan_glmer(learn ~ gender.x + age.x + racecollapse + pubben + water_exaggeratedbinary + gettested + elevbll + (1 | unique_id), data = child_adult, family = "binomial", seed = 26,
                               prior = cauchy(location = 0,
                                              scale = 2.5,
                                              autoscale = TRUE))

mysum <- summary(learn_model2, pars = c("(Intercept)", "gender.xMale", "age.x", "racecollapseOther", "racecollapseWhite", "pubben", "water_exaggeratedbinary", "gettestedYes", "elevbllYes", "Sigma[unique_id:(Intercept),(Intercept)]"), probs = c(0.025, 0.5, 0.975), digits = 2)

mysum

subdat <- data.frame("Outcome" = rep("Learning delays", 8), "Variable" = c("Male gender (ref: Female gender)", "Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Receives public benefits (ref: No benefits)", "Water crisis was exaggerated (ref: Crisis not exaggerated)", "Child screened for BLLs (ref: Child not screened)", "Child diagnosed with elevated BLLs (ref: Child had normal BLLs)"), "Estimate" = mysum[2:9, 5], "Lower" = mysum[2:9, 4], "Upper" = mysum[2:9, 6])
